
%   \documentclass[defaultstyle]{thesis}
%   \documentclass[typewriterstyle]{thesis}
%   \documentclass[modernstyle]{thesis}
    \documentclass[modernstyle,12pt]{thesis}

   %\documentclass[modernstyle,11pt]{thesis}
%   \documentclass[defaultstyle,12pt]{thesis}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%    load any packages which are needed    %%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\usepackage{latexsym}       % to get LASY symbols
\usepackage{rotating}       % for sideways tables/figures
\usepackage{eufrak}
\usepackage{epsfig}     % to insert PostScript figures
\usepackage{amsmath}
\usepackage{tcolorbox}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{color}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{pifont}
\usepackage{hyperref}

 
\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}

\lstset { %
    language=C,
    backgroundcolor=\color{black!5}, % set backgroundcolor   
    commentstyle=\color{codegreen},
    numberstyle=\tiny\color{codegray},
    stringstyle=\color{codepurple},
    basicstyle=\footnotesize,
    breakatwhitespace=false,         
    breaklines=true,                 
    captionpos=b,                    
    keepspaces=true,                 
    numbers=left,                    
    numbersep=5pt,                  
    showspaces=false,                
    showstringspaces=false,
    showtabs=false,                  
    tabsize=2
}


%%%%%%%%%%%%       all the preamble material:       %%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title{\uppercase{Immediate Files System in Minix Operating system}}

\degree{{\emph{\uppercase{Bachelor of Technology}}}}        %  #1 {long descr.}
    {B.Tech., Computer Science and Engineering}     %  #2 {short descr.}

\dept{Department of}            %  #1 {designation}
    {ComputerScience  And Engineering}      %  #2 {name}

\advisor{}{\uppercase{Dr Murali Krishnan}}           %  #1 {title}


\acknowledgements{  \OnePageChapter % *MUST* BE ONLY ONE PAGE!
We would like to express our gratitude and appreciation to all those who helped
us complete this project. First and foremost, we would like to thank our project
guide Dr Murali Krishnan, for his guidance and encouragement. We would also like
to thank Sharath Hari N and Sudev A C, passouts of 2014 batch for their help in
getting us started with the project.\\
\\
\emph{PRAGATI MAAN} \\
\emph{SHRISHTY CHANDRA}
}

% a 1-page Table of Contents ??
 \ToCisShort

\abstract{  \OnePageChapter % one page only ??

     In most of the computer systems, accessing disk files acts as the bottleneck
    in performance. So while designing the we try to minimise the
    number of disk accesses. Immediate file is one solution to this problem.
    The idea is to store files of small size in the inode itself, instead of
    storing the pointers to the disk blocks. Once the size of the file exceeds the memory
    available for block pointers in the inode, it is converted to a regular
    file. This also saves the disk block, which would otherwise have been wasted
    to store a very small size of data ie. internal fragmentation.
     Minix is an operating system that was basically created for educational
     purposes. It consists of a microkernel that is considered to be highly reliable. 
    We aim at implemeting the immediate file system in minix 3.2,
    which includes an abstract layer called the virtual file system besides the minix file system }

%\LoSisShort
%\emptyLoS % no List of Symbols at all ??

%\LoFisShort % a 1-page List of Figures ??
% \emptyLoF % no List of Figures at all ??

%\LoTisShort % a 1-page List of Tables ??
% \emptyLoT % no List of Tables at all ??
%\LoAisShort
%\LoA
% \emptyLoA % no List of Abbreviations at all ??
%\emptyLos  % no List of symbols
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%       BEGIN DOCUMENT...         %%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%  Weird footnotes??
%%%%  default=\arabic; \roman, \Roman, \alph, \Alph, \fnsymbol
%   \renewcommand{\thefootnote}{\fnsymbol{footnote}}
%   \setcounter{footnote}{0}

\begin{document}

\input macros.tex
\input ch3.tex
\input ch1.tex
\input ch2.tex
\input ch4.tex
%% all chapters can be input like this....%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%  Bibliography %%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\bibliographystyle{acm}   % or "siam", or "alpha", or "abbrv"
\nocite{*}      % list all refs in database, cited or not.

\bibliography{refs}     % bib database in "refs.bib"

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%  Appendices %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\appendix   % don't forget this line if you have appendices!
%\input appA.tex
%% all appendices included in this manner%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%   THE END   %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}
